Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-04-20 krs-survey.tex
Formatting of the summary table

\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{supertabular}
\usepackage{pdflscape} %% Used for very big table
\usepackage{moreverb}
\usepackage[table]{xcolor}
\usepackage{listings}
\usepackage{paralist}
\usepackage{fancyhdr}
\usepackage[draft]{fixme}
\fxsetup{footnote}
\fxsetup{nomargin}

@@

%\begin{tabularx}{\textheight}{p{2cm}p{4cm}p{3cm}p{4cm}p{2.3cm}p{2cm}p{2cm}}
\begin{tabular}{p{4.5cm}|ccccccccc}
\hiderowcolors

{} & {\sc KnowRob} & {ORO} & {\sc PEIS} & {\sc CAST} & {\sc Golog} & {\sc NKRL} & {\sc GSM} & {\sc OMRKF} & {\sc DY-KNOW} \\

\hline
\showrowcolors
{\bf Expressiveness} & & & & & & & & &  \\
Logical formalism & Prolog & OWL-DL & {\sc CycL} &  &  &  & & Horn clauses & \\
Expressive power & & & & & & & & &  \\
OWA/CWA & CWA & OWA & & & & & & & \\
Modeling uncertainty & +++ (extension) & & & & & & & + (\emph{candidate} entities) & \\
Meta-cognition & ++ & ++ & & & & & & & \\
{\bf Model} & & & & & & & & &  \\
Representation of space & & & & & & & & ++ &  \\
Representation of temporality & & & & & & & & + &  \\
Context & & & & & & & & ++ &  \\
Alternative worlds & & +++ & & & & & & &  \\
Introspection & + (SRDF) & & & & & & & &  \\
Memory & & + & & & & & & &  \\
{\bf Reasoning} & & & & & & & & &  \\
Standard FOL reasoning & +++ & +++ & & & & & & &  \\
Knowledge structure alteration & & ++ & & & & & & &  \\
Lazy evaluation & +++ & & & & & & & &  \\
Reasoning under uncertainty & ++ (extension) & & & & & & & & \\
Non-monotonic reasoning & & & & & & & & &  \\
Presupposition accomodation & & & & & & & +++ & &  \\
Prediction, projection, diagnosis & & & & & & & & &  \\
Physics-based reasoning & +++ (extension) & & & & & & & &  \\
Planning & + & +++ (external module) & & & & & & &  \\
Learning & & & & & & & & &  \\
{\bf Knowledge Acquisition} & & & & & & & & &  \\
Acquisition techniques & & & & & & & & &  \\
Grounding & & & & & & & & &  \\
Instanciation & & & & & & & & &  \\
{\bf Integration} & & & & & & & & &  \\
...with sensori-motor layers & & & & & & & & &  \\
...with executive layers & & & & & & & & &  \\
Monitoring and debugging & & & & & & & & &  \\
Performances & & & & & & & & &  \\

>>>>

\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{supertabular}
\usepackage{multirow}
\usepackage{varwidth}

\newcommand{\turn}[3][10em]{% \turn[<width>]{<angle>}{<stuff>}
  \rlap{\rotatebox{#2}{\begin{varwidth}[t]{#1}\bfseries#3\end{varwidth}}}%
  }

\usepackage{pdflscape} %% Used for very big table
\usepackage{moreverb}
\usepackage[table]{xcolor}
\usepackage{listings}
\usepackage{paralist}
\usepackage{fancyhdr}
\usepackage[draft]{fixme}
\fxsetup{footnote}
\fxsetup{nomargin}

@@

\begin{landscape}
\begin{table}
\begin{center}

\begin{tabular}{cp{4.5cm}ccccccccc}
\toprule
\multicolumn{2}{c}{\bf Category} & {\sc KnowRob} & {ORO} & {\sc PEIS} & {\sc CAST} & {\sc Golog} & {\sc NKRL} & {\sc GSM} & {\sc OMRKF} & {\sc DY-KNOW} \\

\midrule

\multirow{5}{0.7cm}[-0.2cm]{\turn[1.5cm]{90}{\bf Expressive power}} & Logical formalism & Prolog & OWL-DL & {\sc CycL} &  &  &  & & Horn clauses & \\
 & Expressive power & & & & & & & & &  \\
 & OWA/CWA & CWA & OWA & & & & & & & \\
 & Modeling uncertainty & +++ (extension) & & & & & & & + (\emph{candidate} entities) & \\
 & Meta-cognition & ++ & ++ & & & & & & & \\
\hline
\multirow{6}{0.2cm}{\turn{90}{\bf Model}} & Representation of space & & & & & & & & ++ &  \\
 & Representation of temporality & & & & & & & & + &  \\
 & Context & & & & & & & & ++ &  \\
 & Alternative worlds & & +++ & & & & & & &  \\
 & Introspection & + (SRDF) & & & & & & & &  \\
 & Memory & & + & & & & & & &  \\
\hline
\multirow{10}{0.2cm}{\turn{90}{\bf Reasoning}} & Standard FOL reasoning & +++ & +++ & & & & & & &  \\
 & Knowledge structure alteration & & ++ & & & & & & &  \\
 & Lazy evaluation & +++ & & & & & & & &  \\
 & Reasoning under uncertainty & ++ (extension) & & & & & & & & \\
 & Non-monotonic reasoning & & & & & & & & &  \\
 & Presupposition accomodation & & & & & & & +++ & &  \\
 & Prediction, projection, diagnosis & & & & & & & & &  \\
 & Physics-based reasoning & +++ (extension) & & & & & & & &  \\
 & Planning & + & +++ (external module) & & & & & & &  \\
 & Learning & & & & & & & & &  \\
\hline
\multirow{3}{0.7cm}{\turn[1cm]{90}{\bf Knw. acq.}} & Acquisition techniques & & & & & & & & &  \\
 & Grounding & & & & & & & & &  \\
 & Instanciation & & & & & & & & &  \\
\hline
\multirow{4}{0.2cm}{\turn{90}{\bf Integ.}} & ...with sensori-motor layers & & & & & & & & &  \\
 & ...with executive layers & & & & & & & & &  \\
 & Monitoring and debugging & & & & & & & & &  \\
 & Performances & & & & & & & & &  \\

\bottomrule
